\paragraph{Conclusion of work}
There are 3 members in our group. Li Tong and Zhong Yuqing are responsible for UI design. Which also includes implementing UI design into xml activity format, linking UI and collect bugs reported from tester. Liu Xinhong is responsible for the app logic, class design and class implementation. Testing is conducted by all members.  All of us are conscientious and good at cooperating. 
                                
\paragraph{Comment on the result and completion level}
After all the developments, our app is complicated and contains a great number of functions, which is coincident with our original planning ideas. For instance, we discussed about the functions like emergency calling, artificial voice reminder, adding friends and measuring the instant heart rate, etc. Such functions are all implemented successfully. Although there are still some issues we cannot resolve well in the end,  they somehow do not affect much to our app. By the way, we didn’t put up our app on the “Google Play” because it needs an external device which would not be owned by most of the users.  
 
\paragraph{Feedbacks}
We have shown our app to our classmates, friends and relatives. Some people think our app is fairly good and user friendly, and they like the style of our user interface; some consider our app as a useful heath assistant which reminds them to pay attention to their heart conditions; some students regard the sensor as an accurate mearusing tool while others think it is a little expensive and may not want to afford it. In addition, there are also some advises like we should add more attributes to predict the heart diseases, not only the heart rate. It would be better to improve the ranking page, for example, add a function to view the detail scores of our friends. 

All in all, we are pretty satisfied with our achievement, as well as how valuable experience we had gained from the process of developing “IntoHeart”. 
