Based on your use cases, derive functions of your app that must be implemented to allow a user to perform the tasks. A function is described as a set of inputs, the behaviour, and outputs. 

\begin{itemize}

\item System shall show the start page then Dashboard(Normal Mode). \textless User open the "Into Heart" app\textgreater
\item System shall show the navigation menu. \textless User press the menu button or slides to right\textgreater 
\item System shall let user allow the Bluetooth and connect to the sensor. \textless User press "Sensor" in menu\textgreater 
\item System shall show the user information and could modify them. \textless User press the "My info" in menu and press "Save" button\textgreater 
\item System shall let user input username, E-mail, password to create a new account. \textless User press "Create An Account" in "My info"\textgreater 
\item System shall let user input E-mail and password and log in the account. \textless User press "Log in" in "My info"\textgreater 
\item System shall jump to user page where not logged in. \textless User press "Sign Out" in "My info"\textgreater 
\item System shall show heart rate diagram of instant, day, week, month respectively. \textless User press "Instant Heart Rate", "Day", "Week", "Month" in "Dashboard", respectively\textgreater 
\item System should show exercise mode and give an artificial voice reminder. \textless User press "Exercise Mode" on "Dashboard" when it is in "Normal Mode"\textgreater 
\item System should give a warning voice reminder or even call the emergency number. \textless User's heart rate is out of regular range\textgreater 
\item System shall show the setting window and user could toggle whether enable the emergency call. \textless User press setting button at right corner\textgreater 
\item System shall show average, minimum, maximum of recent heart rate, as well as predicted kind of heart disease. \textless User press "Analysis" in menu\textgreater 
\item System shall show popup window of diseases and could search for wikipedia. \textless User press "View tachycardia details" or "View bradycardia details" and enter into any diseases\textgreater 
\item System shall show ranking page, which calculates users' total \endnote{American Heart Association, retrieved from 
http://www.heart.org/HEARTORG/GettingHealthy/\\PhysicalActivity/FitnessBasics/Target-Heart-Rates\_UCM\_434341\_Article.jsp on Apr 10, 2015 }score and makes comparisons. \textless User press "Ranking" in menu\textgreater 
\item System shall show adding friend page and could search for new friends. \textless User press add friends button on "Ranking"\textgreater 
\item System shall show the life record page. \textless User press "Life Style" in menu\textgreater 
\item System shall popup windows to record life habit. \textless User press either five icons and change the rating bar\textgreater 

\end{itemize} 
